Untitled

### 2019-06-03 Manuscript_draft/phylo_signal_table.Rmd
phylo results

lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
lambda<- as.numeric(lambda)
p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
p <- as.numeric(p)
trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "**Stigma length**", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
table<- data.frame(lambda,p, trait)
colnames(table) <- c("Lambda", "P-value", "Traits")
kable(table, format="markdown")
```

>>>>

lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
lambda<- as.numeric(lambda)
p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
p <- as.numeric(p)
trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "Stigma length", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
table<- data.frame(lambda,p, trait)
colnames(table) <- c("Lambda", "P-value", "Traits")
kable(table, format="markdown", digits = 2)
```

library(kableExtra)
load("Data/img_phylo_no_conv.RData")

lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
lambda<- as.numeric(lambda)
p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
p <- as.numeric(p)
trait <- c("Selfing rate", "Pollen size", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "SI index")
table<- data.frame(lambda,p, trait)
colnames(table) <- c("Lambda", "P-value", "Traits")
kable(table, format="markdown", digits = 2)
```
